A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-29 paper/draft.tex
add final section regarding patronage

In total, we achieve the match of 18.5 million unique matches between the the \emph{RAIS} dataset and the party membership data. To give a sense of the scale of the data ETL (extraction, transformation and loading): in the year of 2015 there were in total 54 million employees in the \emph{RAIS} data, while in the party membership there were 9.2 million active membership ties. Partitioning the data into manageable chunks requires the development of both a semantic layer and data pipelines that are often beyond the scope of political science and enter the domain of data science and functional programming that fall under the domain of computer science.\footnote{For great resources on the topic, see the following \href{https://r4ds.had.co.nz/index.html}{\emph{R for Data Science}} resource.}

\subsection{Who enters the bureaucracy?}

Why do politicians engage in patronage? And who should politicians buy off? There are competing views on who benefits from patronage, and what is motivating it in the first place. On the one hand, from a politician's perspective it can be cheaper to buy voters who are poor, insofar as these voters need and value more monetary incentives \citet{stokes2013brokers}. Other scholars argue that in order to maximize electoral returns, politicians target swing voters, those who are indifferent to either party and therefore, again, require the least resources to buy off \citet{dixit1996determinants}.

@@

\section{Campaign Finance and the Need for Wealthy Patrons}
Municipal elections are expensive. In 2016, municipal races commanded an average amount of \emph{X} amounts of dollars. In order to finance these races, politicians rely on a variety of resources, and at the local level, these are primarily party-member donations. In particular, while in the larger municipalities there is a greater reliance on corporate donations, for the majority of smaller municipalities, the contribution are in large part individual-level contributions.\

Figure \emph{x} illustrates this pattern.

\section{Empirical strategy}
\label{sec:empirical}
The previous sections present suggestive evidence of systematic differences acros partisan and non-partisan members. In particular, party members seem to be wealthier, less educated and concentrated in the upper strata of the local bureaucracy. However, it is not clear from these aggregate statistics whether the higher compensation is due to

In this section, I perform a simple Oaxaca decomposition to pin down heterogeneous compensation across party and non-partisan members with respect to observables. In particular, I model wages as a function of age, work experience, education level and gender. To allow for greater flexibility with respect to compensation across states, I perform the decomposition broken down by state, and allow coefficients to vary by state, year, and

\emph{perform an Oaxaca decomposition to understand the variant compensations}

>>>>

In total, we achieve the match of 18.5 million unique matches between the the \emph{RAIS} dataset and the party membership data. To give a sense of the scale of the data ETL (extraction, transformation and loading): in the year of 2015 there were in total 54 million employees in the \emph{RAIS} data, while in the party membership there were 9.2 million active membership ties. Partitioning the data into manageable chunks requires the development of both a semantic layer and data pipelines that are often beyond the scope of political science and enter the domain of data science and functional programming that fall under the domain of computer science.\footnote{For great resources on the topic, see the following \href{https://r4ds.had.co.nz/index.html}{\emph{R for Data Science}} resource.} The entire data pipeline is documented \href{https://github.com/galileukim/ego_patronage}{here}.

\subsection{Who benefits from patronage?}

Why do politicians engage in patronage? And who should politicians buy off? There are competing views on who benefits from patronage, and what is motivating it in the first place. On the one hand, it can be cheaper to buy voters who are poor, insofar as these voters need and value more monetary incentives \citet{stokes2013brokers}. Other scholars argue that in order to maximize electoral returns, politicians target swing voters, those who are indifferent to either party and therefore, again, require the least resources to buy off \citet{dixit1996determinants}.

@@

\section{Campaign Finance and Wealthy Patrons}
Municipal elections are expensive to finance. In 2016, municipal races commanded an average amount of \emph{X} amounts of dollars. In order to pay for these electoral races, politicians rely on a variety of resources, and at the local level, these are primarily party-member donations. In particular, while in the larger municipalities there is a greater reliance on corporate donations, for the majority of smaller municipalities, the contribution are in large part individual-level contributions. Securing access to wealthy patrons willing to donate is key

Figure \emph{x} illustrates this pattern. It shows for the year 2008, the only year in which there is data on the electoral title available, who donates to politicians.

\begin{figure}
    \centering
    \includegraphics[width = 8cm, height = 8cm]{figures/partisanship/plot_contribution.pdf}
    \caption{\textbf{Breakdown of Individual Donation by Party Membership.} We }
\end{figure}

% \section{Empirical strategy}
% \label{sec:empirical}
% The previous sections present suggestive evidence of systematic differences acros partisan and non-partisan members. In particular, party members seem to be wealthier, less educated and concentrated in the upper strata of the local bureaucracy. However, it is not clear from these aggregate statistics whether the higher compensation is due to

% In this section, I perform a simple Oaxaca decomposition to pin down heterogeneous compensation across party and non-partisan members with respect to observables. In particular, I model wages as a function of age, work experience, education level and gender. To allow for greater flexibility with respect to compensation across states, I perform the decomposition broken down by state, and allow coefficients to vary by state, year, and

% \emph{perform an Oaxaca decomposition to understand the variant compensations}
